---
output: 
  html_document:
    toc: true
    toc_float: 
      collapsed: false
  number_sections: true
 
title: ""
author: "[User-764Q](https://github.com/User-764Q)"
date: "`r paste0('Last Run: ', format(Sys.time(), '%A %d-%B-%Y'))`"
params: 
  param1: "Don't Forget about params"

---

<style>

#TOC {
 font-family: Calibri; 
 font-size: 16px;
 border-color: #3D68DF;
 background: #3D68DF;
}

body {
  font-family: Garamond;
  font-size: 16px; 
  border-color: #D0D0D0;
  background-color: #D0D0D0;
  color: #1A1A1A;
}

pre {
  color: #1A1A1A
  background: #D0D0D0;
  background-color: #D0D0D0
  font-family: Calibri; 
  
}

</style>

# Lvl 3 Police Stations NZ 

#### Feb 2021

This project was to practice two things, plotting some geographic data and scraping some web data. 

* Data for police stations is scrapped from google, via google outscraper. 

* The geographic boundary file is the TA border from [Stats NZ](https://datafinder.stats.govt.nz/layer/104267-territorial-authority-2020-generalised/)

After plotting the police stations a geo-join to official border region is done to find only those stations that are in the Alert level 3 boundary. 

```{r, include=FALSE}

# default chunk settings for Knit. 

knitr::opts_chunk$set(
  echo = TRUE, warning = FALSE, message = FALSE
)
```

```{r, setup and load}

## Loading packages

library(tidyverse)
library(lubridate)
library(ggthemes)
library(tmap)
library(sf)

#Loading Police station locations these are from 'Auckland' according to google. 
#But some likely fall outside the area

police_data <- read_delim('Auckland_police_station.csv', delim = ',', skip = 1) %>%
  st_as_sf(coords = c('longitude', 'latitude'), crs = 4326)

# Creating the path for the stats NZ territory data
path_to_ta_shapefile <- file.path('statsnzterritorial-authority-2020-generalised-CSV' , 
                                  'territorial-authority-2020-generalised.csv') 

# Loading the lockdown area data
Lock_down_area <- read_delim(path_to_ta_shapefile, delim = ',') %>%
    st_as_sf(wkt = 'WKT', crs = 2193) %>%
    # filtering just Auckland 
    filter(TA2020_V1_00_NAME == 'Auckland') 

```

### Initial plot

The web scraping just looked at stations that mentioned 'Auckland' so it's expected that some of them are not in the official boundary. Less likely is missing some stations because they are in the boundary but don't mention Auckland. 4 Stations are not in the area and will be removed. 

```{r}

# Initial plot

  ggplot() + 
    geom_sf(data = Lock_down_area) +
    geom_sf(data = police_data)

```

### In the area only

This code removes the stations that are not in the boundary. 

```{r}

# 

# need to reprgramme crs to match. 

police_data_2193 <- police_data %>% st_transform(crs = 2193)

joined_data <- st_join(Lock_down_area, police_data_2193)
in_area_police <- joined_data %>% pull(full_address)

in_area_police_2193 <- police_data_2193 %>%
  filter(full_address %in% in_area_police) 


```

### Plotting by 'City'

Re plotting with only those stations in the official boundary, colouring by 'City'.

```{r, replot}

tmap_mode('plot')

tm_shape(Lock_down_area) + tm_polygons(col = 'cornflowerblue', alpha = .5) + 
  tm_shape(in_area_police_2193) + tm_dots(col = 'query_p2', size = .2) +
  ggsave('lock_down_stations.png', device = jpeg)

```

